---
title: "Final Report"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# Final Report

1. 13 pages of text
2. 6 graphs/tables

## Basics of time series (when and why we use them, basic terminology) (1-2 pages)

## Autoregressive models (1-2 pages)

## Moving average models (1-2 pages)

## Real-world Application using one of the above techniques (8 pages)

### An overview of dataset, why a time series model is appropriate

(1-2 page)

### Fitting AR and MR models to the data, explaining the parameters and why I choose them

(4-5 pages)

### Discussion & Conclusion
(2-3 pages)

## Forecasting. Key concepts and applying on dataset (2-3 pages)

## Conclusion and looking into the future (1 page)

```{r}
library(quantmod)
getSymbols("CPIAUCSL", auto.assign = TRUE, src = "FRED")
getSymbols("USSTHPI", auto.assign = TRUE, src = "FRED")
CPI <- read.csv("data/CPIAUCSL.csv")
USHousePriceIndex <- read.csv("data/USSTHPI.csv")

plot(CPIAUCSL)
plot(USSTHPI)
```

